Diagnosis Visualizations

### 2023-05-24 Diagnosis_Vis.Rmd
treatment duration boxplot

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")
```

@@

>>>>

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

view(Mothership)
```

@@

# Duration of treatment based upon disorder

Source for [Data_Vis](https://twitter.com/nrennie35/status/1655911610618114052)
```{r}
library(tidyverse)
#install.packages("showtext")
library(showtext)
# install.packages("camcorder")
library(camcorder)
# install.packages("ggtext")
library(ggtext)
library(glue)
# install.packages("nrbrand")
#require(nrBrand)
    #what the fuck is this?
# install.packages("ggmagnify")
#library(ggmagnify)

font_add_google("Fredericka the Great", "fred")
showtext_auto()

# gg_record(
#   dir = file.path("~/Desktop/Coding/R working directory/plots/Recording"), # where to save the recording
#   device = "png", # device to use to save images
#   width = 8, # width of saved image
#   height = 6.5, # height of saved image
#   units = "in", # units for width and height
#   dpi = 300 # dpi to use when saving image
# )

bg_col <- "#F9FBF2"
# highlight_col <- "#FFAD05"
# highlight_col <- "FF52825"
highlight_col <- "#02d46e"
outline_col <- "darkblue"
dark_col <- "#333333"

title = "Length of Treatment for Different Disorders"
st = "The partial hospitalization program at the Rhode Island Hospital consists of a variety of treatment modalities for psychiatric disorders, but mainly consists of mindfulness based psychotherapies (e.g., ACT). Patients come for treatment during the day from 9-5 and do not stay overnight in the hospital. Patient discharge is agreed between psychiatrist, therapist, and patient."

cap = "**Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "

set.seed(12345)
ggplot(
  data = Mothership_Current_Long,
  mapping = aes(
    x = Days_complete_1,
    y = Disorder_Type,
    group = Disorder_Type)
  )+
  geom_jitter(
    size = 0.6,
    alpha = .5,
    colour = highlight_col
    )+
  geom_boxplot(
    outlier.shape = NA,
    colour = outline_col,
    fill = highlight_col,
    alpha = 0.3) +
  scale_x_continuous(
   breaks = c(0, 15, 30, 45, 60),
    limits = c(0.00, 60)
  ) +
  labs(
    x = "Number of Days In Partial Hospitalization Program",
    y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = st,
    caption = cap
    ) +
  theme_minimal(
    base_size = 30,
    base_family = "Commissioner"
    ) +
  theme(
    axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4,
       colour = alpha(dark_col, 0.2),
    ),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 20),
      colour = dark_col,
      size = 70
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 20),
      halign = 0,
      size = 28
    ),
    plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10)
    ),
    axis.text = element_text(colour = dark_col),
    axis.title = element_text(colour = dark_col),
    legend.position = "none",
    plot.margin = margin(15, 15, 10, 10)
  )

```
